Lonely and online: an investigation of social media use and social isolation in China

### 2024-06-10 tandf/Social-Isolation-in-China-jg-revised.tex
updated files from jg

\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

@@

\title{Lonely and online: an investigation of social media use and
social isolation in China}
\author{}
\date{2024-06-10}

\begin{document}
\maketitle
\begin{abstract}
Research on the link between social media and well being has lead to
ambiguous findings - some research has found a positive, negative, and
mixed relationship between the two. We employ the case of China, in
which social media is controlled in important ways, as a useful
alternative case to gain leverage on these ambiguities. Using data from
a nationwide survey of Chinese citizens (n=2292), we principally find
that individual, heterogeneous effects are an important driver of the
relationship between levels of social media use and reported well-being.
Additionally, our results lend support to a FOMO (fear of missing out)
mechanism as an important driver of the relationship while not finding
support for the mechanism of exposure to negative content on social
media as a predictor of well-being. Finally, our findings suggest that
institutional context may not play an important role in the social media
- social isolation relationship.
\end{abstract}

@@

\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-latex/fig-social-iso-dist-1.pdf}

@@

\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-latex/fig-var-dist-1.pdf}

@@

\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-latex/fig-sm-use-dist-1.pdf}

@@

\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-latex/fig-urban-dist-1.pdf}

@@

\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-latex/fig-social-isolation-interactions-1.pdf}

@@

\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-latex/fig-resids-human-1.pdf}

@@

\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-latex/fig-resids-online-offline-1.pdf}

>>>>

\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

@@

\begin{document}
\title{Lonely and online: an investigation of social media use and
social isolation in China}

\author{\name{\textsuperscript{a} and }
\affil{\textsuperscript{a}
\textsuperscript{b}}}

\maketitle

\begin{abstract}
Research on the link between social media and well being has lead to
ambiguous findings - some research has found a positive, negative, and
mixed relationship between the two. We employ the case of China, in
which social media is controlled in important ways, as a useful
alternative case to gain leverage on these ambiguities. Using data from
a nationwide survey of Chinese citizens (n=2292), we principally find
that individual, heterogeneous effects are an important driver of the
relationship between levels of social media use and reported well-being.
Additionally, our results lend support to a FOMO (fear of missing out)
mechanism as an important driver of the relationship while not finding
support for the mechanism of exposure to negative content on social
media as a predictor of well-being. Finally, our findings suggest that
institutional context may not play an important role in the social media
- social isolation relationship.
\end{abstract}

\begin{keywords}
    Social Isolation, Social Media, Digital Communication, 
    China
\end{keywords}
\newpage{}

@@

\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-social-iso-dist-1.pdf}

@@

\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-var-dist-1.pdf}

@@

\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-sm-use-dist-1.pdf}

@@

\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-urban-dist-1.pdf}

@@

\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-social-isolation-interactions-1.pdf}

@@

\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-resids-human-1.pdf}

@@

\includegraphics{Social-Isolation-in-China-jg-revised_files/figure-pdf/fig-resids-online-offline-1.pdf}
